Simulations of Ballot Polling Risk-Limiting Audits

### 2022-05-12 providence/sections/pilot.tex
pilot table

% pilot
A pilot audit was performed in Providence, Rhode Island in February 2022 from November 2021 special elections.
The audited contest was a question on School Construction and Renovation Projects which had an announced $25.67\%$ margin.
The risk-limit was $10\%$.
A large first round size of $140$ with probability of stopping $95\%$ was selected in order to give many ballots for more interesting analysis afterwards.

>>>>

% pilot
A pilot audit was performed in Providence, Rhode Island in February 2022 of November 2021 special elections.
The audited contest was a yes-or-no question on School Construction and Renovation Projects and had an announced $25.67\%$ margin.
The risk-limit was $10\%$.
A first round size of $140$ ballots with large probability of stopping ($95\%$) was selected, and selection order was tracked, in order to give the potential for more interesting analysis afterwards. 
As expected, the audit concluded in the first round with a \Providence risk of $4.18\%$. Table~\ref{fig:pilot-risks} shows risk measures for the drawn sample using \Minerva and \BRAVO (both EoR and SO).

\begin{figure}
\begin{center}
\begin{tabular}{ |c|c|c|c|c| } 
\hline
%\diagbox[dir=NW]{First \\Round \\Size}{RLA}
ballots& \rotatebox{45}{\Providence} & \rotatebox{45}{\Minerva} & \rotatebox{45}{EoR \BRAVO} & \rotatebox{45}{SO \BRAVO} \\
\hline
140 & \bf{4.18\%} & \bf{4.18\%} & \bf{5.41\%} & 36.6\% \\
\hline
\end{tabular}
\end{center}
\caption{Risk measures for the drawn first round of $140$ ballots in the Providence, RI pilot audit. Risks in bold meet the risk-limit ($10\%$) and thus correspond to audits that would stop.}
\label{fig:pilot-risks}
\end{figure}

TODO: Add examples of how the audits perform for various hypothetical round schedules. I wait to do this until I'm done with the workload estimates since the examples here should be chosen to motivate that section.

### 2022-05-12 providence/sections/related.tex
pilot table

In \BRAVO, $p_0=\frac{1}{2}$. If testing the \BRAVO stopping condition after each individual ballot
is drawn (a \B \BRAVO audit), clearly $\sigma$ is equivalent to the 
likelihood ratio:
$$
\frac{Pr[K=k|H_a,n]}{Pr[K=k|H_0,n]}= \frac{\binom{n}{k}p_a^{k} (1-p_a)^{n-k}}{\binom{n}{k}(\frac{1}{2})^n} =\sigma(k, p_a, \frac{1}{2}, n)
$$

>>>>

In \BRAVO, $p_0=\frac{1}{2}$. If testing the \BRAVO stopping condition after each individual ballot
is drawn (a \B \BRAVO audit), $\sigma$ is equivalent to the 
likelihood ratio:
$$
\frac{Pr[K=k|H_a,n]}{Pr[K=k|H_0,n]}= \frac{\binom{n}{k}p_a^{k} (1-p_a)^{n-k}}{\binom{n}{k}(\frac{1}{2})^n} =\sigma(k, p_a, \frac{1}{2}, n)
$$
